\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-25 OaklandSubmission/intro.tex
cp for 1.0

Today it is hard for developers to create secure implementations using cryptographic techniques.
Typical developers lack an understanding of cryptographic protocols
and cannot be expected to implement them correctly and efficiently without tool
support.
In an ideal world, a developer declares the functionality to be implemented
in a general purpose programming language and an automatic tool takes care
of all the cryptography and generates a secure and efficient implementation  of the functionality. 
This paper provides a language-based solution to make
secure  computation  accessible to the software developer community.

@@

Secure two-party computation (\mpc) \cite{yao,gmw} is a powerful
cryptographic tool that allows two mutually distrusting parties
to compute a joint function of their secret inputs such as {\em secure prediction} \cite{shafindss,wu,barni,minionn,secureml}. Here,  one party holds the propriety classifier for disease, genomics or spam detection and the other party  
holds the private input and the second party learns the classification label such as the presence of the disease. Since its introduction
\mpc in 1980's, there has been a long sequence of work that has
transformed \mpc from a mere theoretical tool to something practically
efficient and usable. Hence, there have been efforts to make \mpc
accessible to non-specialist programmers. To understand the
state-of-the-art, let us consider the following 
example that is the sub-computation in many classification tasks.

Suppose a developer wants to compute $w^Tx >b$ securely using
\mpc, where $w$ and $x$ are two vectors, $b$ is a scalar, and $w^Tx$ denotes the inner product of $w$ and $x$.  With the current techniques, he has three options. \aseem{We should
  use she for the programmer instead of he?}
\begin{tiret}
\item He can code up the functionality in a programmer friendly
  domain-specific language such as
  \cite{lambdaps,wysteria,oblivm,smcl,cbmcgc} that would automatically
  compile it to a \mpc protocol. The downside is that all of these
  works build on a cryptographic back-end that takes as input a functionality expressed as either a boolean circuit \cite{yao,gmw} or an arithmetic circuit \cite{homo}.
  The efficiency of the generated \mpc protocol is hence, bounded by the possibility of efficiently representing the functionality in one of these circuit representations. For instance, multiplication of two $\ell$-bit integers can be expressed as a boolean circuit of size  $O(\ell^2)$ or an arithmetic circuit with 1 multiplication gate. 
Hence, for better efficiency, we would like to securely compute $w^Tx$ using an arithmetic circuit and the comparison with $b$ using a boolean circuit. \divya{that is not supported by above systems.}
In fact, most interesting functions require a mix of arithmetic and boolean computations for efficiency.

\item To address this issue of efficient representation, recently Demmler et al. \cite{aby} gave a cryptographic protocol for \mpc where the functionality can be expressed as a circuit with a mix of both arithmetic and boolean parts.
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, in their framework, the programmer is required to write circuits consisting of  arithmetic and boolean gates along with appropriate
inter-conversion gates.
This requires the programmer to be aware of
trade-offs between arithmetic and boolean cryptographic
schemes as well as the complex inter-conversion costs between arithmetic and boolean, and manually split the functionality into such parts accordingly.  
In short, as is also mentioned by Demmler et al., the current system  is not suitable
to be used by non-specialist programmers without security expertise.

\item Finally, the third option is to hire a cryptographer to design a specialized efficient protocol for this functionality such as \cite{shafindss,wu,minionn}. 
\end{tiret}
In our work, we achieve the best of all the above options.

>>>>

Today it is hard for the developers to program secure applications
using cryptographic techniques. Typical developers lack a deep
understanding of the cryptographic protocols, and therefore cannot be
expected to use them correctly and efficiently on their own.
Ideally, a developer would declare the functionality in a general
purpose, high-level programming language and a
tool, e.g. a compiler, would generate an efficient protocol that
implements the functionality securely, while hiding the cryptography
behind-the-scenes. This paper presents such a framework for Secure
Two-party Computation (\mpc).

@@

\mpc~(\cite{yao,gmw}) is a powerful
cryptographic technique that allows two mutually distrusting parties
to compute a joint function of their secret inputs in a way that both
the parties learn nothing about the inputs of each other beyond what
is revealed by their (possibly different) outputs. For example, \mpc
can be used for {\em secure
prediction}~(\cite{shafindss,wu,barni,minionn,secureml}),
where one party (the server) holds a proprietary classifier to predict
a label (e.g. a disease, genomics, or spam detection), and the other
party (the client) holds a private input that it wants to run the
classifier on. Using \mpc guarantees that the server learns nothing
about the client's input or output, and that the client learns nothing
about the server model, beyond what is revelaed by the output
label.

Since its introduction in 1980s, there has been a long sequence
of work that has transformed \mpc from a mere theoretical concept to
something practically efficient and usable. To understand the
state-of-the-art, let us consider the following example used by many
secure prediction algorithms. Suppose Alice wants to write
a \mpc protocol to securely
compute $w^Tx >b$. Here $w$ and $x$ are two vectors (inputs of the two
parties), $b$ is a scalar, $\cdot^{T}$ is the matrix transpose
operator, and $w^Tx$ denotes the inner product of
$w^{T}$ and $x$.  With the current state-of-the-art, Alice has three
options:

%\begin{tiret}
%\item

She can program the computation in one of the several programmer
friendly, domain-specific languages (such
as~\cite{lambdaps,wysteria,oblivm,smcl,cbmcgc}) that would
automatically compile it to a \mpc protocol. However, all of these
frameworks use cryptographic backends that take as input
the computation expressed as either a boolean
circuit~(\cite{yao,gmw}) or an arithmetic circuit~(\cite{gentry}).
%
The efficiency of the generated \mpc protocol is thus bounded by the
efficiency of representing the computation in one of
these representations. For instance, multiplication of two
$\ell$-bit integers can be either expressed as a boolean circuit of
size $O(\ell^2)$, or as an arithmetic circuit with 1 multiplication
gate.
%
Hence, for better efficiency, Alice would ideally like to compute
$w^Tx$ using an arithmetic circuit, and the comparison with $b$ using
a boolean circuit.
%
Unfortunately, none of the above frameworks support combinations of
arithmetic and boolean circuits, and using different tools for
different parts of the computation is cumbersome and error-prone.

%% In fact, most interesting functions require a mix of arithmetic and
%% boolean computations for efficiency.

%\item

Alternatively, Alice can use a tool such as ABY (Demmlet et
al.~\cite{aby}) that allows
the computation to be expressed as a combination of arithmetic and
boolean circuits. However, here the programming interface is quite
low-level -- the programmer is required to first manually split the
computation into arithmetic and boolean components, and then write the
circuits for all the componenets manually, including the appropriate
inter-conversion gates between them. Clearly, writing correct
and efficient protocols in such a framework is beyond an average
programmer who does not understand the various trade-offs between
arithmetic and boolean circuits, and even for an expert cryptographer,
writing large computations in such a framework can be tedious and
error-prone (a sentiment also echoed by Demmler et al.~\cite{aby}).

%\item
The third option for Alice is to earn a PhD in cryptography and design
specialized, efficient protocols (similar to
~\cite{shafindss,wu,minionn}) for her tasks.
%\end{tiret}
%In our work, we achieve the best of all the above options.
